Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
Some discussions and conclusions

\usepackage[pdftex]{hyperref}
\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\newcommand{\ea}{{et~al.}\xspace}

@@

In this study we wanted to understand whether analysts have a bias in how they recall precise data.
Before we analyze the bias between what participants remembered from the approximate and precise visualizations, we look at the relative errors (absolute bias) independently.
We removed outliers where the relative bias was larger than 4 times the standard deviation using sigma clipping.
Table \ref{table_errors} summarized the results.
Since we expect a bias (R1), the errors in the precise visualization should be larger.
The errors for the type 1 questions were significantly larger ($p=0.0002$ for type 1), while we could not see a significant effect of type 2 questions.  \todo{What's happening? These errors are waaaay too large.}

@@

@@

\subsection{Threads to Validity} %I would opt to put this under the experimental setup, but I understand that Mike might want differently.

We had no way of ensuring that participants did not take screenshots or notes in order to answer later questions about the precise visualizations.
\todo{some more detail here, now that we collected data}

\section{Conclusion}
The conclusion goes here \todo{when we have data}.

>>>>

\usepackage[pdftex]{hyperref}
\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\newcommand{\secref}[1]{\hyperref[#1]{Section~\ref*{#1}}}
\newcommand{\tabref}[1]{\hyperref[#1]{Table~\ref*{#1}}}
\newcommand{\ea}{{et~al.}\xspace}

@@

In this study we wanted to understand whether analysts have a bias in how they recall precise data.
Before we analyze the bias between what participants remembered from the approximate and precise visualizations, we look at the relative errors (absolute bias) independently.
We removed outliers where the relative bias was larger than 4 times the standard deviation using sigma clipping.
\tabref{table_errors} summarized the results.
Since we expect a bias (R1), the errors in the precise visualization should be larger.
The errors for the type 1 questions were significantly larger ($p=0.0002$ for type 1), while we could not see a significant effect of type 2 questions.  \todo{What's happening? These errors are waaaay too large.}

@@

\todo{Explain why we see the bias}
\todo{Talk about massive error}

\subsection{Threats to Validity} %I would opt to put this under the experimental setup, but I understand that Mike might want differently.

We had no way of ensuring that participants did not take screenshots or notes in order to answer later questions about the precise visualizations.
Although we asked participants to not take notes during the study, a few self-reported that they did.
We removed these participants from the data but we don't know whether any other participant took notes in secret.
Another problematic factor is the large error for type 2 questions (see \tabref{table_errors}).
This could be because participants misunderstood the task or because they ignored the instructions.

\section{Conclusion}

In this study, we found that exposure to approximate data prior to seeing the precise data biases the observations people make.
This has important implications for the design of applications that present approximate results as well as for journalists who report for example polls before votes.
In this paper we tried to reduce the bias by making people aware of the approximate result they have previously seen but we did not see a significant reduction of the bias.
In future work, we should focus of usable methods to reduce the bias that can be used by approximate visualization tools and journalists.

@@
